---
title: "Case Study"
author: "Murrel Pereira"
date: "10/19/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width ="90%"
)

theme_set(theme_minimal() + theme(legend.position="bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Load the airbnb data

```{r}
data("nyc_airbnb")
```

##Brainstorm some questions

*What is the best Airbnb in Staten Island for <$100?
*What price range is popular in each borough? Most rented?
*What apartment features are related to price?
*Cheapest room type in each neighborhood
*Hosts have higher ratings

##

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group) %>% 
  summarize(avg_price =mean(price)) %>% 
  ggplot(aes(x=neighbourhood_group, y=avg_price)) +
    geom_scatter()
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x=neighbourhood_group, y=price)) +
    geom_boxplot()
```

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars=review_scores_location/2)
```

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb %>% 
  filter(
    neighbourhood_group == "Manhattan"
  ) %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(
    price <1000,
    neighbourhood_group == "Manhattan"
  ) %>% 
  mutate(neighbourhood =fct_reorder(neighbourhood,price)) %>% 
  ggplot(aes(x=neighbourhood, y=price)) +
    geom_boxplot() +
    coord_flip()

```

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x=lat, y=long, color=price)) +
  geom_point()
```

##Create a leaflet map
```{r}

pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars))
nyc_airbnb %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius=1, color=~pal(stars))
  
```

```{r}
pal <- colorNumeric("magma", nyc_airbnb %>% pull(stars))
nyc_airbnb %>% 
  drop_na(stars) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(stars))
```